Thread Pool in GeckoDB/BOLSTER

### 2018-06-07 Presentations/Milestone3/presentation.tex
Add Milestone 3 presentation (not complete)

\title{Thread Pool in GeckoDB/BOLSTER}
\subtitle{Milestone II: Concept \& additional literature research}
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise, Benedikt Zeilinger}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

% Milestone II: Concept & additional literature research

@@

\section{Previously...}
\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{itemize}
		\item Operations are spawning dozens of threads, which are not handled and managed
		\item Heavy overhead of creating and removing threads
		\item After some operations profiler dies (too many threads)
		\item Because of Late/Early Materialization and Prefetching Support, existing libs are not adequate
	\end{itemize}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{img/thumbs_down.png}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{itemize}
		\item Reuse of Threads with thread pools.
		\item Reduce overhead of thread management
		\item Improve maintainability of parallel code
		\item Support the performance and design requirements (e.g. Future and Promise) of BOLSTER
	\end{itemize}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{img/thumbs_up.png}
	\end{center}
\end{frame}

\section{Concept and Design}
\begin{frame}
	\frametitle{Concept}
	\begin{itemize}
		\item Thread pool with runtime dynamic amount of threads and priority queue
		\item Tasks are not preemtable and independent
		\item Array of tasks passed to an enqueue function, which waits until all tasks are finished
		\item Threads without tasks idle until they get a new one
		\item Monitoring/managing state and assigned task of each thread
		\item Allow usage of multiple, independent thread pool instances 
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Design}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_queue.png}
	\end{center}
\end{frame}

\section{Current Progress}
\begin{frame}
	\frametitle{Current Progress}
	We...
	\begin{itemize}
		\item Implemented the priority queue 
		\item Implemented the creation of threads and the assigning of tasks
		\item Added gtest framework to project and wrote tests for pool and queue
		\item Began first implementations of waiting for tasks to be finished
		\item Measure performance of task assigning and execution
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Wait for task - Problem}
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\begin{itemize}
				\item Problem: waiting for a task to complete could lead to a
				race condition
				\item This was caused by the uncertainty of a thread\_task
				during transition between the priority queue and the
				thread pool
				\item Solution: slotmap with an atomic counter
			\end{itemize}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=1.0\textwidth]{waitingconcept.png}
		\end{column}
	\end{columns}
\end{frame}

\section{Next Steps}
\begin{frame}
	\frametitle{Next Steps}
	We have to ...
	\begin{itemize}
		\item Find an efficient way to idle threads until they get the next tasks
		\item Add metrics to threads and tasks and measure performance and overhead
		\item Add tests for all implementations
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Next Steps - Scheduling}
	Current approach:  
	\begin{itemize}
		\item Threads ask for next task in queue
	\end{itemize}
	Desired implementation: 
	\begin{itemize}
		\item Make own scheduling, assign tasks to threads
		\item Add possibility to try different scheduling approaches
		\item Measure thread idle and busy time for the approaches
	\end{itemize}
\end{frame}

\section{Additional Literature Research}
    \begin{frame}
        \frametitle{Additional Literature Research}
        \begin{itemize}
            \item Albahari, Joseph. \emph{Threading in C\#.} online. Joseph Albahari \& O’Reilly Media, Inc (2006).
            \item Rasmussen, Rasmus V., and Michael A. Trick. \emph{Round robin scheduling–a survey.} European Journal of Operational Research 188.3 (2008): 617-636.
            \item Shreedhar, Madhavapeddi, and George Varghese. \emph{Efficient fair queueing using deficit round robin.} ACM SIGCOMM Computer Communication Review. Vol. 25. No. 4. ACM, 1995.
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{Thank you for your attention!}
	    \includegraphics[width=\textwidth]{img/important.jpg}
    \end{frame}
\end{document}

>>>>

\title{Thread Pool in GeckoDB/BOLSTER}
\subtitle{Milestone III: Implementation \& evaluation setup}
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise, Benedikt Zeilinger}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

@@

\section{Previously...}
\begin{frame}
	\begin{center}
		\huge Previously...
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_queue.png}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\begin{itemize}
				\item Problem: waiting for a task to complete could lead to a
				race condition
				\item This was caused by the uncertainty of a thread\_task
				during transition between the priority queue and the
				thread pool
				\item Solution: slotmap with an atomic counter
			\end{itemize}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=1.0\textwidth]{waitingconcept.png}
		\end{column}
	\end{columns}
\end{frame}

\section{Implementation}
\begin{frame}
	\begin{center}
		\huge Implementation
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Design of Thread Pool System}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_structure.png}
	\end{center}
	\begin{itemize}
		\item Thread pool system contains priority queue and thread pool itself
		\item Performance monitoring as optional, external component
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Implementation}
	We...
	\begin{itemize}
		\item Implemented task enqueueing and execution
		\item Implemented performance monitoring as external component
		\item Added gtest framework to project and wrote tests for pool and queue
		\item Started writing performance tests and measures for comparison against baseline ???
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Open issues}

\end{frame}

\section{Evaluation Setup}
\begin{frame}
	\begin{center}
		\huge Evaluation Setup
	\end{center}
\end{frame}

\begin{frame}
    \frametitle{Thank you for your attention!}
 	\includegraphics[width=\textwidth]{img/important.jpg}
\end{frame}

\end{document}
